Simulation conditionnelle d’un processus gaussien

### 2022-05-19 tex/article_template.tex
Revert "Pauline's addition"
This reverts commit 6e4efca80e43d0d6c12c3b5a2b41af9c2a7992eb.

>>>>

\begin{thebibliography}{9}
\bibitem{coursgeo}
Yann Méneroux (2018), \emph{Introduction à la Géostatistique}, Institut National de l'Information Géographique et Forestièr
\bibitem{texbook}
Donald E. Knuth (1986) \emph{The \TeX{} Book}, Addison-Wesley Professional.

\bibitem{acc rej}
Karl Sigman (2007), \emph{Acceptance-Rejection Method}

\bibitem{inv transform}
Karl Sigman (2010), \emph{Inverse Transform Method}

\bibitem{krig}
Eric Marcon (2021), \emph{Krigeage avec R}

\bibitem{handbook}
Dikr P. Kroese (2011), Thomas Taimre, and Zdravko I. Botev, \emph{Handbook of Monte Carlo Methods}, Wiley series in Probability and Statistics

\bibitem{variate generation}
Luc Devroye (1986), \emph{Non-Uniform Random Variate Generation}, Springer Science

\bibitem{geo sim}
Christian Lantuéjoul (2002), \emph{Geostatistical Simulation}, Springer

\bibitem{mont methods}
Christian P. Robert, George Casella (1999), \emph{Monte Carlo Statistical Methods Second Edition}, Springer Texts in Statistics

\bibitem{geostat}
Jean-Paul Chilès, Pierre Delfiner (2012), \emph{Geostatistics Modeling Spatial Uncertainty}, Wiley series in Probability and Statistics

\end{thebibliography}
